Centrality and Activity for Envolving Networks

### 2013-06-20 network-science/paper.tex
2

\pgfplotsset{compat=1.6}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}
\usetikzlibrary{positioning}
\usetikzlibrary{automata}
\usepackage{tikz-3dplot}

@@

%>>>
%>>>
\title %<<< Title Region
{
	Centrality and Activity for Envolving Networks
}
\author
{ \normalfont
	Pufan He\\
	\href{mailto:hpfdf@126.com}{hpfdf@126.com}\\
	Tsinghua University.
	\and
	Yichao Zhou\\
	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}\\
	Tsinghua University.
	\and
	Qiwei Feng\\
	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}\\
	Tsinghua University.
	\and
	Yu Yan\\
	\href{mailto:}{}\\
	Tsinghua University.
	\and
	Qingyang Li\\
	\href{mailto:}{}\\
	Tsinghua University.
	\and
	Xin Xing\\
	\href{mailto:}{}\\
	Tsinghua University.
}
\date
{
	June 25, 2013
}
%>>>

\begin{document}
\maketitle
\newpage
\begin{abstract}

\end{abstract}

>>>>

%\pgfplotsset{compat=1.6}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}
\usetikzlibrary{positioning}
\usetikzlibrary{automata}
\usepackage{tikz-3dplot}

@@

%>>>
%>>>
\title %<<< Title Region
{
	Metrics and Algorithms for Envolving Social Networks
}
\author
{
	Pufan He\\
	\href{mailto:hpfdf@126.com}{hpfdf@126.com}
	\and
	Yichao Zhou\\
	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}
	\and
	Qiwei Feng\\
	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}
	\and
	Yu Yan\\
	\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com}
	\and
	Qingyang Li\\
	\href{mailto:591527324@qq.com}{591527324@qq.com}
	\and
	Xin Xing\\
	\href{mailto:823291634@qq.com}{823291634@qq.com}
}
\date{}
%>>>

\begin{document}
\maketitle
\newpage
\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered to be vertex while friendship is considered to be edge.
\end{abstract}
